Monte Carlo calculation to characterize neutron and gamma fields for ANITA neutron facility at TSL

### 2015-04-17 Paper2015.tex

\section{Modelling}
Simulations were conducted using Geant4 version 10.0 and the binary intranuclear cascade model, as recommended in~\cite{Platt13}.
A detailed model of the ANITA geometry was implemented in Geant4, as illustrated in Fig.~\ref{fig:ANITAoverview}
Description of the geometry is given in \cite{Prokofiev2009,Prokofiev14}.
%; a summary only is given here.
%The spallation target is a tungsten cylinder of diameter \SI{5}{\cm} and length \SI{2.4}{\cm}.
%The target is cooled by water and surrounded by a stainless-steel cooling jacket.
%The target assembly with its cooling jacket appears as a small blue rectangle in Fig.~\ref{fig:ANITAoverview}.
%Lead shielding blocks in the target region are also modelled, and shown in red Fig.~\ref{fig:ANITAoverview}.
%A large electromagnet surrounding the target is modelled and shown in Fig.~\ref{fig:ANITAoverview} in grey (iron) and yellow (copper).
%An iron collimator with variable apertures is modelled  and shown downstream of the target (grey).
Except where indicated otherwise, all results in this summary are for the standard collimator size (\SI{10.2}{\cm} diameter).
In the final paper we will present results for cylindrical collimators in the range from \SIrange{3}{30}{\cm} diameter.
Simulated protons were incident axially at an energy of \SI{180}{\MeV}.
Resulting gamma and neutron fields were evaluated at several detector locations.
In this paper results are presented for three of these: the Standard User Position (SUP), \SI{2.5}{\m} downstream of the target centre\todo{check centre}~\cite{Prokofiev2009}, the Close User Position (CUP), \SI{0.75}{\m} downstream of the target, and the CUP-TOF, \SI{0.84}{m} downstream of the target.
The SUP and CUP positions are of interest as they are positions used for SEE tests; the CUP-TOF position is the location of thin-film breakdown counter (TFBC) detectors used for beam monitoring and characterisation using time-of-flight (TOF) techniques.
Model validation will be demonstrated against CUP-TOF data (section~\ref{tbd}).

@@

\subsection{Neutron fluence rate, spatial distribution and spectrum}
Fig.~\ref{fig:SUPDensity} shows neutron spatial distribution at the SUP, for neutrons above \SI{10}{\MeV}.
The collimation effect is clearly visible.
Fig.~\ref{fig:SUPProfile} shows neutron fluence profile at the SUP.
In Fig.~\ref{fig:SUPProfile} simulated data were folded in energy with the neutron fission cross section for \U238~\cite{tbd}, replicating measurement with a \U238\ TFBC~\cite{Prokofiev2009}.
Within the beam umbra the predicted neutron fluence rate above \SI{10}{\MeV} at a proton current of \SI{200}{\nA} is \SI{0}{\neutron\per\cm\squared\per\second}, compared to \SI{0}{\neutron\per\cm\squared\per\second} from earlier calculations~\cite{Platt13} and \SI{0}{\neutron\per\cm\squared\per\second} from the parameterisation~\cite{Prokofiev2009}.
The parameterisation therefore exceeds the current calculations by tbd\%.\todo{Quantify integral yield}

@@

>>>>

\section{Modelling}
Simulations were conducted using Geant4 version 10.0 and the binary intranuclear cascade model, as recommended in~\cite{Platt13}.
A detailed model of the ANITA geometry was implemented in Geant4, as illustrated in Fig.~\ref{fig:ANITAoverview}
Description of the geometry is given in \cite{Prokofiev2009,Prokofiev14}.
%; a summary only is given here.
%The spallation target is a tungsten cylinder of diameter \SI{5}{\cm} and length \SI{2.4}{\cm}~\cite{ANITAdrawing}.
%The target is cooled by water and surrounded by a stainless-steel cooling jacket.
%The target assembly with its cooling jacket appears as a small blue rectangle in Fig.~\ref{fig:ANITAoverview}.
%Lead shielding blocks in the target region are also modelled, and shown in red Fig.~\ref{fig:ANITAoverview}.
%A large electromagnet surrounding the target is modelled and shown in Fig.~\ref{fig:ANITAoverview} in grey (iron) and yellow (copper).
%An iron collimator with variable apertures is modelled  and shown downstream of the target (grey).
Except where indicated otherwise, all results in this summary are for the standard collimator size (\SI{10.2}{\cm} diameter).
In the final paper we will present results for cylindrical collimators in the range from \SIrange{3}{30}{\cm} diameter.
Simulated protons were incident axially at an energy of \SI{180}{\MeV}.
Resulting gamma and neutron fields were evaluated at several detector locations.
In this paper results are presented for three of these: the Standard User Position (SUP), \SI{2.5}{\m} downstream of the target centre\todo{check centre, it said that 250cm downstream of the production target in the paper}~\cite{Prokofiev2009}, the Close User Position (CUP), \SI{0.75}{\m} downstream of the target, and the CUP-TOF, \SI{0.84}{m} downstream of the target.
The SUP and CUP positions are of interest as they are positions used for SEE tests; the CUP-TOF position is the location of thin-film breakdown counter (TFBC) detectors used for beam monitoring and characterisation using time-of-flight (TOF) techniques.
Model validation will be demonstrated against CUP-TOF data (section~\ref{tbd}).

@@

\subsection{Neutron fluence rate, spatial distribution and spectrum}
Fig.~\ref{fig:SUPDensity} shows neutron spatial distribution at the SUP, for neutrons above \SI{10}{\MeV}.
The collimation effect is clearly visible.
Fig.~\ref{fig:SUPProfile} shows neutron fluence profile at the SUP.
In Fig.~\ref{fig:SUPProfile} simulated data were folded in energy with the neutron fission cross section for \U238~\cite{tbd}, replicating measurement with a \U238\ TFBC~\cite{Prokofiev2009}.
Within the beam umbra the predicted neutron fluence rate above \SI{10}{\MeV} at a proton current of \SI{200}{\nA} is \SI{7.1e5}{\neutron\per\cm\squared\per\second}, compared to \SI{5.7e5}{\neutron\per\cm\squared\per\second} from earlier calculations~\cite{Platt13} and \SI{9.3e5}{\neutron\per\cm\squared\per\second} from the parameterisation~\cite{Prokofiev2009}.
The parameterisation therefore exceeds the current calculations by tbd 31\%.\todo{Quantify integral yield}

@@

\bibitem{ANITAdrawing}
Prokofiev, A.V. 
\newblock personal communication
\newblock {\em TSL, Sep. 2013}
